Guarded Recursion in Agda via Sized Types

### 2019-01-15 code-oneclock-paper/latex/paper.tex
rephrased sizes
Reamed some titles
Added a conclusion

\section{Presheaf Semantics}
Next we define categorical semantics for the syntax defined in \Cref{sec:syntax}.
To do so, we use a similar method as used by M{\o}gelberg \cite{Mogelberg14}.
The interpretation of types depend on the clock contexts.
If the clock context is empty, then types become sets.
If the clock context has one clock, then types are interpreted as objects in the topos of trees.

@@

\subsection{Kripke Semantics}
%\label{sec:kripke}
\input{CloTT/Structure/Contexts}

@@

\subsection{Inductive Types}
\input{CloTT/TypeFormers/Mu}

\section{The Interpretation}
\input{GuardedTT}

\section{Conclusion}

>>>>

\section{Categorical Semantics}
Next we define categorical semantics for the syntax defined in \Cref{sec:syntax}.
To do so, we use a similar method as used by M{\o}gelberg \cite{Mogelberg14}.
The interpretation of types depend on the clock contexts.
If the clock context is empty, then types become sets.
If the clock context has one clock, then types are interpreted as objects in the topos of trees.

@@

\subsection{Simple Type Theory in Presheaves}
%\label{sec:kripke}
\input{CloTT/Structure/Contexts}

@@

\subsection{Guarded Recursive Types}
\input{CloTT/TypeFormers/Mu}

\section{Consistency}
\input{GuardedTT}

\section{Conclusion}
We formally defined a syntax of guarded type theory with explicit substitutions and weakening, and we constructed denotational semantics for it in type theory extended with sized types.
From this, we concluded that this theory is consistent and that guarded recursion can be defined via sized types.

There are several possible ways to improve on this result.
First of all, one could define a dependent version of this type theory extended with multiple clocks.
This can be done in two ways.
Either one extends the object theory with delayed substitutions \cite{bizjak2016guarded} or with ticks \cite{BahrGM17}.
Second of all, with the deep embedding in place, one can further study the meta-theory by defining a formalized type checking and a normalization algorithm.
